\package{}: an \R{} package for implemetation of the ITHIM model

### 2016-09-14 manuscript/manuscript.tex
Updates to manuscript
abstract changes

\section{Summary:}
\col[blue]{We divided the U.S. metropolitan regions into 10 regions defined by
the Department of Health and Human Services (HHS1-10).  We performed a
comparative risk analysis for each of the regions using national
averages as the baseline.  We investigated the active transport
component of the ITHIM model by estimating regional travel parameters
using the National Household Transportation Survey.  The West coast
and the Northeast of the U.S. have travel patterns that, if mirrored
by the nation, would save the U.S. thousands to hundreds of thousands
DALYs.}

@@

\section{Introduction}
\col{ITHIM is a statistical model that integrates data on travel patterns,
physical activity, fine particulate matter, GHG emissions, and disease
and injuries. Based on population and travel scenarios. The model has
been used to calculate the health impacts of walking and bicycling
short distances usually traveled by car or driving low-emission
automobiles \cite{woodcock2013,maizlish2013}.}

@@

>>>>

\section{Summary:}
\col[blue]{While increased active transportation, primarily cycling and walk, is often held up as a goal for improved public health — via reduced chronic disease, improved air quality, and reductions in greenhouse gas emissions — obtaining estimates for the quantiative impacts of such shifts remains infrequent, in not altogether absent. Using U.S. metropolitan counties from  the 10 regions defined by
the Department of Health and Human Services (HHS1-10) we perform a
comparative risk analysis between each regions and national
averages as the baseline.  We investigated the reduced chronic disease burden of (x,y,z outcomes) from increased physical activity from population shifts in the amount of biking and walking doen for transport. 
Our methods employ the Integrated Transport and Health Impacts Model (ITHIM) informed by regional travel parameters
using the National Household Transportation Survey, non-travel activity metircs from the American Time Use Survey, and baseline Disease burden from the Centers for Disease Control and Prevention's WONDER database.  Our findings show that the West coast
and the Northeast of the U.S. have travel patterns that, if mirrored
by the nation, would save the U.S. thousands to hundreds of thousands
DALYs.}

@@

\section{Introduction}
\col{}

\col{ITHIM is a statistical model that integrates data on travel patterns,
physical activity, fine particulate matter, GHG emissions, and disease
and injuries. Based on population and travel scenarios. The model has
been used to calculate the health impacts of walking and bicycling
short distances usually traveled by car or driving low-emission
automobiles \cite{woodcock2013,maizlish2013}.}

@@

The ITHIM model uses the comparative risk assesment framework
